---
title: "test"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.width = 8,
                      fig.height = 6)
```

```{r}
library(shiny)
# runExample("01_hello")
```

```{r}
# runApp("App-1")
# runApp("App-2")
# runApp("App-3")
# runApp("census-app", display.mode = "showcase")
```

```{r}
# counties <- readRDS("census-app/data/counties.rds")
# head(counties)
```

```{r}
# install.packages(c("maps", "mapproj"))
```

```{r}
# library(maps)
# library(mapproj)
# source("census-app/helpers.R")
# counties <- readRDS("census-app/data/counties.rds")
# percent_map(counties$white, "darkgreen", "% White")
```

- Source scripts, load libraries, and read data sets at the beginning of app.R outside of the server function.

- Define user specific objects inside server function, but outside of any render* calls. 

- Only place code that Shiny must rerun to build an object inside of a render* function.

```{r}
# runApp("census-app", display.mode = "showcase")
```

```{r}
# install.packages("quantmod")
```

```{r}
# runApp("stockVis")
```

# test weighting shiny

```{r}
library(shiny)
runApp("weighting", display.mode = "showcase")
```

```{r}
library(tidyverse)
data = read_csv("weighting/data/example.csv")
categorical_vars = c("strata", "age_grp")
weight_var = "weight"
response_var = "HbA1c"
```

```{r}
if (!all(c(response_var, weight_var, categorical_vars) %in% names(data))) {
    stop("One or more specified columns are not present in the data.")
  }

data[categorical_vars] <- lapply(data[categorical_vars], as.factor)

summary(data)

# Create a formula for the model
formula <- as.formula(paste("!is.na(", response_var, ") ~", paste(categorical_vars, collapse = " + ")))

print(formula)

ps_model <- glm(formula, data = data, family = binomial(link = "logit"))
```

```{r}
source("weighting/helpers.R")
sample = propensity_score_adjustment(
  data = data,
  response_var = response_var,
  weight_var = weight_var,
  categorical_vars = categorical_vars
)
sample
```

```{r}
library(tidyverse)
data = read_csv("weighting/data/example.csv")
categorical_vars = c("strata", "age_grp")
continuous_vars = c("BMI")  
weight_var = "weight"
response_var = "response"
```

```{r}
library(CHAID)
set.seed(2025)

# Check if the required columns are present
if (!all(c(response_var, weight_var, categorical_vars) %in% names(data))) {
  stop("One or more specified columns are not present in the data.")
}

data = data[,c(categorical_vars, weight_var, response_var)]

# Convert categorical variables to factors
data[categorical_vars] <- lapply(data[categorical_vars], as.factor)

# Create a formula for the model
formula <- as.formula(paste0("factor(", response_var, " == 1) ~ ", paste(categorical_vars, collapse = " + ")))

chaidobj <- chaid(formula, data = data)

plot(chaidobj)

classes <- predict(chaidobj)

#### Calculate weight by using the unweighted response rate in each terminal node of the tree
chaid_pw = data.frame(data, rclass = attributes(classes)$names) %>% 
  group_by(rclass) %>% 
  mutate(
    m = sum(.data[[response_var]])/length(.data[[weight_var]]),
  ) %>% 
  ungroup() %>% dplyr::select(m) %>% unlist(use.names = FALSE)

data$rclass = attributes(classes)$names

data$WT_chaid = 1 / chaid_pw

## Construct the new weight
data$adjW_chaid = data$weight * data$WT_chaid
```

```{r}
library(rpart)
set.seed(2025)

# Check if the required columns are present
if (!all(c(response_var, weight_var, categorical_vars) %in% names(data))) {
  stop("One or more specified columns are not present in the data.")
}

data = data[,c(categorical_vars, weight_var, response_var)]

# Convert categorical variables to factors
data[categorical_vars] <- lapply(data[categorical_vars], as.factor)

# Create a formula for the model
formula <- as.formula(paste0("factor(", response_var, " == 1) ~ ", paste(categorical_vars, collapse = " + ")))

cart.tree = rpart(response, data = data, method = "class")

## CART fitted values and assign weights
cart.fitted = predict(cart.tree, type="prob")

data$cart.wt = 1/cart.fitted[,2]
data$adjW_cart = data[[weight_var]] * data$cart.wt
```


```{r}
library(BART)
set.seed(2025)

# Check if the required columns are present
if (!all(c(response_var, weight_var, categorical_vars, continuous_vars) %in% names(data))) {
  stop("One or more specified columns are not present in the data.")
}

if(length(intersect(continuous_vars, categorical_vars)) > 0) {
  stop("Continuous variables should not overlap with categorical variables.")
}

# delete rows with missing values in the covariates
bart_data = data[complete.cases(data[c(weight_var, categorical_vars, continuous_vars, response_var)]), ]

y_train = bart_data[[response_var]]
X_train = bart_data[, c(categorical_vars, continuous_vars)]


str(y_train)
str(X_train)


# use Probit BART
fit_bart = pbart(x.train = as.data.frame(X_train), y.train = y_train)
str(fit_bart)

data$WT_probit = 1 / fit_bart$prob.train.mean
data$WT_probit[response_var == 0] = 0

# Construct the new weight
data$adjW_probit = data$weight * data$WT_probit
data
```

```{r}
library(xgboost)
set.seed(2025)

# Check if the required columns are present
if (!all(c(response_var, weight_var, categorical_vars, continuous_vars) %in% names(data))) {
  stop("One or more specified columns are not present in the data.")
}

if(length(intersect(continuous_vars, categorical_vars)) > 0) {
  stop("Continuous variables should not overlap with categorical variables.")
}

# Prepare data for xgboost

# data = data[,c(categorical_vars, weight_var, continuous_vars, response_var)]

model_data = data %>%
  select(all_of(c(continuous_vars, categorical_vars, weight_var, response_var))) %>%
  na.omit()  

# Convert categorical variables to factors
y = model_data[[response_var]]
X = model.matrix(~ . -1, data = model_data %>% select(-c(response_var, weight_var)))  


dtrain = xgb.DMatrix(data = X, label = y)

# Train the XGBoost model
xgb_fit = xgboost(data = dtrain,
                  objective = "binary:logistic",
                  nrounds = 100,
                  max_depth = 3,
                  eta = 0.1,
                  verbose = 0)

pred_probs = predict(xgb_fit, newdata = dtrain)

model_data$WT_xgboost = 1 / pred_probs
model_data$WT_xgboost[response_var == 0] = 0

## Construct the new weight
model_data$adjW_xgboost = model_data[[weight_var]] * model_data$WT_xgboost
```

# generate data 

```{r}
library(tidyverse)
data = read_csv("weighting/data/example.csv")
data.complete = data[is.na(data$HbA1c)==FALSE,]
write.csv(data.complete, file = "example_2.csv", row.names = FALSE)
```

```{r}
library(shiny)
runApp("weighting", display.mode = "showcase")
```

```{r}
# data = read_csv("weighting/data/example_2.csv")
# install.packages("rpart.plot") 
# install.packages("egg")
```

without weight
correlation graph
calibration
lay out
table download and view
if name is not "weight"
error message
question mark (example for data, match )

superlearner
graph
histogram
theme (whithe background and black grid)


1. warning 
2. reference & intepretation
3. analysis data visulation  
4. download + show lines
5. bubble plot
6. superlearner
7. preface
8. machine learning
wed 10:30

12.10 
model based approach
Thur 9:30

new variablde in CHAID
shap
lime
active plot

home -> steps introduction instruction how it looks like ? which method recommendation 
what you want ? which tab is useful for u.



data input -> initial weights before adjustment 
wed 9:30


CHAID CART
MENU
NAME WEIGHT AND response

9:30 -10 wed